---
output: html_document
---



<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
div.gray { background-color:#1f68cf; border-radius: 5px; padding: 20px;}
</style>
<div class = "gray">


<style>
div.blue { background-color:#cfc5ab; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

### [Back](http://falconer94.github.io/)

# Personal Finance Script

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br>
My wife and I have several banking accounts and keeping track of everything was kind of sloppy. I wrote this script in order to tidy it up and join the account info into one. I probably shouldn't share the data sets of our personal finances, so I just have the script to demonstrate and share.
<br><br>
First, I import the data sets and join the tables together. Since the CSV data sets are coming from different sources, the columns need to be adjusted.
<br><br>
```{r, eval=FALSE}
library(tidyverse)
library(janitor)
# options(scipen=999)

#### Import ####
sav <- read.csv("Finance_data/month/savings.csv", header = FALSE)
che <- read.csv("Finance_data/month/checking.csv", header = FALSE)
cha_j <- read.csv("Finance_data/month/mine.CSV")
cha_k <- read.csv("Finance_data/month/wife.CSV")



#### Tidy and Join ####

# Columns
# Date, Account, Description, Category, Amount

#### cha_j 
names(cha_j)

cha_j <- cha_j %>% 
  rename(Date = Transaction.Date) %>% 
  select(-Post.Date, -Type, -Memo) %>% 
  add_column(Account = "Chase_mine") 


#### cha_k
cha_k <- cha_k %>% 
  rename(Date = Transaction.Date) %>% 
  select(-Post.Date, -Type, -Memo) %>% 
  add_column(Account = "Chase_wife") 


#### che

che <- che %>% 
  select(-V3, -V4) %>% 
  rename(
    Date = V1,
    Amount = V2,
    Description = V5
  ) %>% 
  add_column(Account = "Checking") 


#### sav
names(sav)
sav <- sav %>% 
  select(-V3, -V4) %>% 
  rename(
    Date = V1,
    Amount = V2,
    Description = V5
  ) %>% 
  add_column(Account = "Savings") 



# Joined

joined <- full_join(cha_j, cha_k) %>% 
  full_join(che) %>% 
  full_join(sav)
```
<br>
After joining the data sets, the descriptions are just sloppy. I use grepl() to search for a portion of text and then override the entire value with something clean and simple. 
<br><br>
The info in the category column is not really useful when most items are in different categories. I use grepl() to search a portion of text in the description again, but instead override the category column with something useful. 
<br><br>
```{r, eval=FALSE}
#### Rename Descriptions ####

joined$Description[grepl("Spotify", joined$Description)] <- "Spotify"
joined$Description[grepl("POWER", joined$Description)] <- "Power"
joined$Description[grepl("Energy", joined$Description)] <- "Energy"
joined$Description[grepl("eDeposit", joined$Description)] <- "Deposit"
joined$Description[grepl("TPM", joined$Description)] <- "HOA"
joined$Description[grepl("TRANSFER", joined$Description)] <- "Online_Transfer"
joined$Description[grepl("MORTG", joined$Description)] <- "Mortgage"
joined$Description[grepl("COMCAST", joined$Description)] <- "Comcast"
joined$Description[grepl("SPROUTS", joined$Description)] <- "Sprouts"
joined$Description[grepl("WAL-MART", joined$Description)] <- "Walmart"
joined$Description[grepl("WM SUPERCENTER", joined$Description)] <- "Walmart"
joined$Description[grepl("AMZN", joined$Description)] <- "Amazon"
joined$Description[grepl("Amazon.com", joined$Description)] <- "Amazon"
joined$Description[grepl("LOWES", joined$Description)] <- "Lowes"



#### Categories ####
# Home, Education, Fun, Hobby, Groceries, 
# Health, Transfer, Monthly, Automotive, Gas, 
# Gifts, Deposit, Work, Interest, Tithing

unique(joined$Category)

### Rename categories
joined$Category[joined$Category == "Entertainment"] <- "Fun"
joined$Category[joined$Category == "Shopping"] <- "Fun"
joined$Category[joined$Category == "Food & Drink"] <- "Fun"
joined$Category[joined$Category == "Travel"] <- "Fun"
joined$Category[joined$Category == "Personal"] <- "Fun"
# joined$Category[joined$Category == "check"] <- "Deposit"
# joined$Category[joined$Category == "Gift"] <- "Gifts"
joined$Category[joined$Category == "Bills & Utilities"] <- "Monthly"
joined$Category[joined$Category == "Health & Wellness"] <- "Health"


### Fill in blank categories
joined$Category[grepl("Power", joined$Description)] <- "Monthly"
joined$Category[grepl("Energy", joined$Description)] <- "Monthly"
joined$Category[grepl("Spotify", joined$Description)] <- "Monthly"
joined$Category[grepl("Mazda", joined$Description)] <- "Monthly"
joined$Category[grepl("Mortgage", joined$Description)] <- "Monthly"
joined$Category[grepl("Comcast", joined$Description)] <- "Monthly"
joined$Category[grepl("HOA", joined$Description)] <- "Monthly"
joined$Category[grepl("Utilities", joined$Description)] <- "Monthly"

joined$Category[grepl("PAYMENT", joined$Description)] <- "Transfer"
joined$Category[grepl("Payment", joined$Description)] <- "Transfer"
joined$Category[grepl("Chase", joined$Description)] <- "Transfer"
joined$Category[grepl("Deposit", joined$Description)] <- "Transfer"
joined$Category[grepl("Ibotta", joined$Description)] <- "Transfer"
joined$Category[grepl("VENMO", joined$Description)] <- "Transfer"
joined$Category[grepl("Online_Transfer", joined$Description)] <- "Transfer"


### Reoder columns
joined <- joined[,c(1,4,3,5,2)]

```
<br>
I then create another table to get the sum of each category, and add the total in a new row. At a quick glance, this table helps us know if our expenses are on track. 
<br><br>
```{r, eval=FALSE}
#### Export  and Analyze ####

# Sum by category
Category_Total <- joined2  %>% 
  group_by(Category) %>% 
  summarize(Amount = sum(Amount)) 

Category_Total2 <- Category_Total %>% 
  adorn_totals()

write.csv(joined, "Finance_data/month/month.csv")
write.csv(Category_Total, "Finance_data/month/month.csv")

# Remove Transfer
joined2 <- joined %>% 
  filter(Category != "Transfer")

#### Unique categories ####
unique(joined2$Category)

```