---
output: html_document
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
div.gray { background-color:#1f68cf; border-radius: 5px; padding: 20px;}
</style>
<div class = "gray">


<style>
div.blue { background-color:#cfc5ab; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

### [Back](http://falconer94.github.io/)



# Exam 3

## Load packages
```{r}
library(tidyverse)
library(GGally)
library(modelr)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

## Load and tidy data
```{r}
df <- mtcars

df$cyl <- as.factor(df$cyl)
```


## Glimpse
```{r}
ggpairs(df)
```


MPG has strong correlations with weight and cylinders. 


## Models
```{r}
mod1 <- glm(data=df, formula = wt ~ mpg)
mod2 <- glm(data=df, formula = wt ~ mpg + cyl)
mod3 <- glm(data=df, formula = wt ~ mpg * cyl)
```

Including cyl in the formula may help give more accurate predictions between wt and mpg. 

## Test models
```{r,eval=FALSE}
summary(mod1)
summary(mod2)
summary(mod3)
```
Looking at the summaries of each potential model shows that mod3 has the lowest P-value, indicating a more probabale model. 

```{r}
mod1mse <- mean(residuals(mod1)^2)
mod2mse <- mean(residuals(mod2)^2)
mod3mse <- mean(residuals(mod3)^2)

mod1mse
mod2mse
mod3mse
```

Mod3 has lowest mean squared error which also indicates a more probable model. 

## Create predictions
```{r}
mod3.pred <- add_predictions(df,mod3,type = "response")
```


## Plot
```{r}
ggplot(mod3.pred,aes(y=mpg,color=cyl)) +
  geom_point(aes(x=wt))+
  geom_line(aes(x=pred))+
  labs(title="Relationship between gas efficiency, weight, and number of cylinders",
       x="Weight (1000 lbs)",y="Gas efficiency (MPG)",color="Cylinders")

```

As the weight and number of cylenders increases, the gas efficiency decreases. The data suggests that the heavier the car is, the more cylinders it needs, and the more gas it uses per mile. Who would've thought?